Real Time Shape Reconstruction for Near Earth Asteroid Landing

### 2018-03-23 abstract.tex
Commit new title

\title{Asteroid shape reconstruction}

@@

\begin{itemize}
    \item Spacecraft missions around asteroid require long periods of mapping
        \begin{itemize}
            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
            \item The current methods rely on sending all data to the ground in order to compute the shape. 
            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
        \end{itemize}
\end{itemize}

\section{Problem Formulation}\label{sec:problem}
In this paper, we consider the landing of a dumbbell model of an under actuated spacecraft onto an asteroid.
The dumbbell model is a well-known representation of a multi body spacecraft.
Furthermore, the dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics. 
The dumbbell spacecraft consists of two masses connected by a massless rod.
This simple model is useful to capture the main characteristics of a wide variety of spacecraft configurations.
Typically, spacecraft have mass concentrated in a central structure, referred to as the bus, which houses the command and control system, actuators, fuel, sensors etc. 
In addition, comparatively light-weight solar panels extend from the bus to provide electrical energy from solar radiation. 
As a result, the distributed mass of the spacecraft is captured with the dumbbell representation.

>>>>

\title{Real Time Shape Reconstruction for Near Earth Asteroid Landing}

@@

% 
\section{Problem Formulation}\label{sec:problem}
In this paper, we consider the landing of a dumbbell model of an under actuated spacecraft onto an asteroid.
The dumbbell model is a well-known representation of a multi body spacecraft.
Furthermore, the dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics. 
The dumbbell spacecraft consists of two masses connected by a massless rod.
This simple model is useful to capture the main characteristics of a wide variety of spacecraft configurations.
Typically, spacecraft have mass concentrated in a central structure, referred to as the bus, which houses the command and control system, actuators, fuel, sensors etc. 
In addition, comparatively light-weight solar panels extend from the bus to provide electrical energy from solar radiation. 
As a result, the distributed mass of the spacecraft is captured with the dumbbell representation.
